### 2019-02-06 reports/thesis/chapters/5_inference.tex
Renamed allnull experiment

In this experiment, a Gaussian image of size $\addNumber{../figures/inference/allnull/Experiment_AllNullGaussianwidth.txt} \times \addNumber{../figures/inference/allnull/Experiment_AllNullGaussianheight.txt}$ was simulated. The sample mean and sample variance of the post filtered test statistics were recorded. This was repeated \addNumber{../figures/inference/allnull/Experiment_AllNullGaussiannrepeat.txt} times by simulating another Gaussian image. Various kernel radiuses from $r = \addNumber{../figures/inference/allnull/Experiment_AllNullGaussianradius1.txt}$ to $r = \addNumber{../figures/inference/allnull/Experiment_AllNullGaussianradiusend.txt}$ were investigated.

\begin{figure}[htp]
	\centering
	\begin{subfigure}[b]{0.49\textwidth}
		\includegraphics[width=\textwidth]{../figures/inference/allnull/Experiment_AllNullGaussianmean.eps}
		\caption{Post filter sample mean}
	\end{subfigure}
	\begin{subfigure}[b]{0.49\textwidth}
		\includegraphics[width=\textwidth]{../figures/inference/allnull/Experiment_AllNullGaussianvariance.eps}
		\caption{Post filter sample variance}
	\end{subfigure}
	\caption{The sample mean and sample variance of the test statistics in a filtered Gaussian image of size $\addNumber{../figures/inference/allnull/Experiment_AllNullGaussianwidth.txt} \times \addNumber{../figures/inference/allnull/Experiment_AllNullGaussianheight.txt}$. The box plots summarise the \addNumber{../figures/inference/allnull/Experiment_AllNullGaussiannrepeat.txt} repeats of the experiment. The dotted lines show the critical region at the 2$\sigma$ level using standard tests for the sample mean and sample variance, assuming independence.}
	\label{fig:inference_allnullgaussian}
\end{figure}

@@

An experiment was conducted to investigate the sample mean and sample variance of the filtered contaminated image. Ideally the sample mean and sample variance should be 0 and 1 respectively. Different radiuses were investigated from $r=\addNumber{../figures/inference/allnull/Experiment_AllNullPlaneradius1.txt}$ to $r=\addNumber{../figures/inference/allnull/Experiment_AllNullPlaneradiusend.txt}$ and repeated \addNumber{../figures/inference/allnull/Experiment_AllNullPlanenrepeat.txt} times.

@@

\begin{figure}[htp]
	\centering
	\begin{subfigure}[b]{0.49\textwidth}
		\includegraphics[width=\textwidth]{../figures/inference/allnull/Experiment_AllNullPlanemean.eps}
		\caption{Post filter sample mean}
	\end{subfigure}
	\begin{subfigure}[b]{0.49\textwidth}
		\includegraphics[width=\textwidth]{../figures/inference/allnull/Experiment_AllNullPlanevariance.eps}
		\caption{Post filter sample variance}
	\end{subfigure}
	\caption{The sample mean and sample variance of the test statistics in a filtered contaminated Gaussian image of size $\addNumber{../figures/inference/allnull/Experiment_AllNullGaussianwidth.txt} \times \addNumber{../figures/inference/allnull/Experiment_AllNullGaussianheight.txt}$. The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = \addNumber{../figures/inference/contamination/gradx.txt} (x-x_0) + \addNumber{../figures/inference/contamination/grady.txt} (y-y_0)$ and $\sigma_0=\addNumber{../figures/inference/contamination/nullstd.txt}$. The box plots summarise the \addNumber{../figures/inference/allnull/Experiment_AllNullPlanenrepeat.txt} repeats of the experiment. The dotted lines show the critical region at the 2$\sigma$ level using standard tests for the sample mean and sample variance, assuming independence.}
	\label{fig:inference_allnullplane}
\end{figure}

>>>>

In this experiment, a Gaussian image of size $\addNumber{../figures/inference/allnull/AllNullGaussian_width.txt} \times \addNumber{../figures/inference/allnull/AllNullGaussian_height.txt}$ was simulated. The sample mean and sample variance of the post filtered test statistics were recorded. This was repeated \addNumber{../figures/inference/allnull/AllNullGaussian_nrepeat.txt} times by simulating another Gaussian image. Various kernel radiuses from $r = \addNumber{../figures/inference/allnull/AllNullGaussian_radius1.txt}$ to $r = \addNumber{../figures/inference/allnull/AllNullGaussian_radiusend.txt}$ were investigated.

\begin{figure}[htp]
	\centering
	\begin{subfigure}[b]{0.49\textwidth}
		\includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussian_mean.eps}
		\caption{Post filter sample mean}
	\end{subfigure}
	\begin{subfigure}[b]{0.49\textwidth}
		\includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullGaussian_variance.eps}
		\caption{Post filter sample variance}
	\end{subfigure}
	\caption{The sample mean and sample variance of the test statistics in a filtered Gaussian image of size $\addNumber{../figures/inference/allnull/AllNullGaussian_width.txt} \times \addNumber{../figures/inference/allnull/AllNullGaussian_height.txt}$. The box plots summarise the \addNumber{../figures/inference/allnull/AllNullGaussian_nrepeat.txt} repeats of the experiment. The dotted lines show the critical region at the 2$\sigma$ level using standard tests for the sample mean and sample variance, assuming independence.}
	\label{fig:inference_allnullgaussian}
\end{figure}

@@

An experiment was conducted to investigate the sample mean and sample variance of the filtered contaminated image. Ideally the sample mean and sample variance should be 0 and 1 respectively. Different radiuses were investigated from $r=\addNumber{../figures/inference/allnull/AllNullPlane_radius1.txt}$ to $r=\addNumber{../figures/inference/allnull/AllNullPlane_radiusend.txt}$ and repeated \addNumber{../figures/inference/allnull/AllNullPlane_nrepeat.txt} times.

@@

\begin{figure}[htp]
	\centering
	\begin{subfigure}[b]{0.49\textwidth}
		\includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlane_mean.eps}
		\caption{Post filter sample mean}
	\end{subfigure}
	\begin{subfigure}[b]{0.49\textwidth}
		\includegraphics[width=\textwidth]{../figures/inference/allnull/AllNullPlane_variance.eps}
		\caption{Post filter sample variance}
	\end{subfigure}
	\caption{The sample mean and sample variance of the test statistics in a filtered contaminated Gaussian image of size $\addNumber{../figures/inference/allnull/AllNullGaussian_width.txt} \times \addNumber{../figures/inference/allnull/AllNullGaussian_height.txt}$. The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = \addNumber{../figures/inference/contamination/gradx.txt} (x-x_0) + \addNumber{../figures/inference/contamination/grady.txt} (y-y_0)$ and $\sigma_0=\addNumber{../figures/inference/contamination/nullstd.txt}$. The box plots summarise the \addNumber{../figures/inference/allnull/AllNullPlane_nrepeat.txt} repeats of the experiment. The dotted lines show the critical region at the 2$\sigma$ level using standard tests for the sample mean and sample variance, assuming independence.}
	\label{fig:inference_allnullplane}
\end{figure}
